A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-20 tex/body.tex
more

Given a signature $\Sig$, $\thD$ refers to the \emph{theory of
datatypes and codatatypes},
which %in addition to $\Sig$
defines a class of $\Sig$-interpretations $\JJJJ$,
namely the ones that satisfy the %axioms --- existence of all infinite codatatype values cannot be axiomatized
properties mentioned in this section, including (co)induction. The interpretations
in~$\JJJJ$ share the same interpretation for constructor terms and correctly
applied selector terms (modulo renaming of domain elements) but may differ on
variables and wrongly applied selector terms.
A formula is $\thD$-\emph{satisfiable} if there
exists an interpretation in $\JJJJ$ that satisfies it.
% otherwise, it is $\thD$-unsatisfiable. (I trust the readers' intelligence when
% it comes to English prefixes like non-, in-, un-, and a-.)

@@

\def\ackname{Acknowledgment}
\ourparagraph{\ackname.}
We owe a great debt to the development team of CVC4,
including Clark Barrett and Cesare Tinelli,
and in particular Morgan Deters,
who jointly with the first author developed the initial version
of the theory solver for datatypes in CVC4.
%
Our present and former bosses, Viktor Kuncak, Stephan Merz, Tobias Nipkow,
Cesare Tinelli, and Christoph Weidenbach, have either encouraged the research on
codatatypes or at least benevolently tolerated it, both of which we are thankful
for.
%
Peter Gammie and Andreas Lochbihler shared their private
theories with us so we could include them in the benchmarks.
Andrei Popescu helped clarify our thoughts regarding the axiomatization of
codatatypes. Dmitriy Traytel took part in discussions about degenerate
codatatypes.
%
Andreas Lochbihler and Mark Summerfield suggested several textual improvements.
The second author's research was partially supported by the Deutsche
Forschungs\-gemein\-schaft (DFG) project
\relax{Hardening the Hammer} (grant Ni\,491\slash 14-1).

>>>>

Given a signature $\Sig$, $\thD$ refers to the \emph{theory of
datatypes and codatatypes},
which %in addition to $\Sig$
defines a class of $\Sig$-interpretations $\JJJJ$,
namely the ones that satisfy the %axioms --- existence of all infinite codatatype values cannot be axiomatized
properties mentioned in this section, including (co)induction. The interpretations
in~$\JJJJ$ share the same interpretation for constructor terms and correctly
applied selector terms (up to renaming of domain elements) but may differ on
variables and wrongly applied selector terms.
A formula is $\thD$-\emph{satisfiable} if there
exists an interpretation in $\JJJJ$ that satisfies it.
% otherwise, it is $\thD$-unsatisfiable. (I trust the readers' intelligence when
% it comes to English prefixes like non-, in-, un-, and a-.)

@@

\def\ackname{Acknowledgment}
\ourparagraph{\ackname.}
We owe a great debt to the development team of CVC4,
including Clark Barrett and Cesare Tinelli,
and in particular Morgan Deters,
who jointly with the first author developed the initial version
of the theory solver for datatypes in CVC4.
%
Our present and former bosses, Viktor Kuncak, Stephan Merz, Tobias Nipkow,
Cesare Tinelli, and Christoph Weidenbach, have either encouraged the research on
codatatypes or at least benevolently tolerated it, both of which we are thankful
for.
%
Peter Gammie and Andreas Lochbihler shared their private
theories with us so we could include them in the benchmarks.
Andrei Popescu helped clarify our thoughts regarding the axiomatization of
codatatypes and indicated related work. Dmitriy Traytel took part in discussions
about degenerate codatatypes.
%
Andreas Lochbihler, Mark Summerfield, and Dmitriy Traytel suggested several
textual improvements. The second author's research was partially supported by
the Deutsche Forschungs\-gemein\-schaft (DFG) project \relax{Hardening the
Hammer} (grant Ni\,491\slash 14-1).
